Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-16 Latex/journal_v1/V4/pr.tex
add latex

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.

Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\begin{alignat}{4}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\mathcal{R}_{u_{(s,i)}}^{max})
+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\kappa_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\varpi_{u_{(s,i)}})\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\xi_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\lambda_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}-\sigma_{q_r}^2 \times 2^{C^{r}_{max}} )\\
&-  \sum\limits_{r=1}^{R} \mathfrak{v}_{r} (P_{r}-P_{max})\\
&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
\end{alignat}
\end{subequations}

>>>>

\begin{equation}\label{RM}

@@

In order to make \eqref{problem} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cr} to $P_r = \sigma_{q_r}^2\times 2^{C^r}$ so the constraint 
\eqref{c15} is changed to
 $P_r \leq \sigma_{q_r}^2\times 2^{C^r_{max}}$.
The combination of equations \eqref{c13} and \eqref{c15} leads to the following equation
\begin{equation}
\begin{split}
\zeta_{r}&= min\{P_{max}, \sigma_{q_r}^2\times 2^{C^r_{max}} \}, \\
P_r &\leq  \zeta_{r}.\\
\end{split}
\end{equation} 
Moreover, the combination of equations \eqref{c13}, \eqref{c16-2} and \eqref{RM} leads to the following equation
\begin{equation}
\begin{split}
\eta_{u_{(s,i)}}&= max\{\mathcal{R}_{u_{(s,i)}}^{max}, \lambda_{u_{(s,i)}}, \varpi_{u(s,i)} \}, \\
\mathcal{\bar{R}}_{u_{(s,i)}} &\geq  \eta_{u_{(s,i)}}.\\
\end{split}
\end{equation}
Assume $\boldsymbol{\mathfrak{v}}$, $\boldsymbol{\mathfrak{m}}$, $\boldsymbol{\mathfrak{h}}$, $\boldsymbol{\xi}$, $\boldsymbol{\chi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.

The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\begin{alignat}{4}
&\mathcal{L}(\boldsymbol{P},\boldsymbol{E}; \boldsymbol{\mathfrak{v}}, \boldsymbol{\chi}, \boldsymbol{\mathfrak{h}}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}, \boldsymbol{\mathfrak{m}})  = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathcal{\bar{R}}_{u_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\mathfrak{h}_{u_{(s,i)}} (\mathcal{\bar{R}}_{u_{(s,i)}}-\eta_{u_{(s,i)}})\\
&-  \sum\limits_{r=1}^{R} \mathfrak{m}_{r} (P_{r}- \zeta_r)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\kappa^k_{r,u(s,i)}  p^k_{r,u(s,i)}\\
&+ \sum\limits_{r=1}^{R}\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\chi_{r,u(s,i)}(\sum_{k =1}^{K_s} e^{k}_{r,u(s,i)} -1)\\
&-  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R}\mathfrak{v}^{k}_{r,u(s,i)} (e^{k}_{r,u(s,i)} -1)\\
&+  \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{U_s}\sum\limits_{k=1}^{K} \sum\limits_{r=1}^{R} \xi^{k}_{r,u(s,i)} e^{k}_{r,u(s,i)}.
\end{alignat}
\end{subequations}
